Boundary Conformal Field Theory

### 2017-04-28 bCFT_paper.tex
add bCFT_paper.tex
[draft]all embedding tikz figures are standalone

\documentclass[preprint, prb]{revtex4-1}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{bm}
\usepackage[font={footnotesize}]{caption}
\usepackage{todonotes}
\definecolor{darkblue}{rgb}{0.1,0.2,0.6} \definecolor{darkred}{rgb}{0.8,0.1,0.2}
\usepackage[colorlinks,citecolor=darkblue,linkcolor=darkred,urlcolor=darkblue]{hyperref}
\usepackage[all]{hypcap}

\renewcommand{\vec}[1]{\boldsymbol{\mathbf{#1}}}

\newcommand{\cf}{\textit{cf.} } 
\newcommand{\ie}{\textit{i.e.} } 
\newcommand{\eg}{\textit{e.g.} }
\newcommand{\vs}{\textit{vs.} } 
\newcommand{\etal}{\textit{et al.} }
\newcommand{\etc}{\textit{etc.} }

\begin{document}

\title{Bipartite Fidelity and Loschmidt echo of bosonic conformal interface}

\author{Tianci Zhou}
\email{tzhou13@illinois.edu}
\affiliation{University of Illinois, Department of Physics, 1110 W. Green St. Urbana, IL 61801 USA}

\author{Mao Lin}
\email{maolin2@illinois.edu}
\affiliation{University of Illinois, Department of Physics, 1110 W. Green St. Urbana, IL 61801 USA}

\date{\today}

\begin{abstract}
\end{abstract}

\maketitle

\section{Introduction}
% the last one to be finished.

\section{Bosonic Conformal Interface}
\subsection{General Formulation}
% M, S
% special case
\subsection{Physical Realization: Connecting Bosons of Different Compactification Radii}
% free boson + compact
\subsection{A Free Boson Lattice Model}
% cite Calabrese, introduce the model
% lattice model S matrix

\section{Bipartite Fidelity and Loschmidt Echo}
\subsection{Definition}
% definition
% general discussion

\section{Analytic and Numerical Results}
\subsection{Fidelity}
% analytic: conformal transformation
% numerical comparison 
\subsection{Loschmidt Echo}
% analytic: conformal transformation
% numerical comparison

\section{Discussion}

\begin{acknowledgments}
\todo[inline]{Thomas Faulkner, Xueda Wen, Shinsei Ryu, Romain Vasseur}
    TZ is supported by the National Science Foundation under grant number NSF-DMR-1306011.
    This work made use of the Illinois Campus Cluster, a computing resource that is operated by the
    Illinois Campus Cluster Program (ICCP) in conjunction with the National Center for
    Supercomputing Applications (NCSA) and which is supported by funds from the University of
    Illinois at Urbana-Champaign.
\end{acknowledgments}

\appendix
\section{Corrections to the Free Energy}
% two corrections:
% 1. staircase geometry
% 2. contribution from the boundary: cite Cardy

\section{Numerical Computation of Bipartite Fidelity and Loschmidt Echo}
% basis transformation, Bogoliubov state, overlap(master theorem)
% Peschel_EE.pdf

\section{A Determinant Identity for the Boundary State Amplitude}
% copy notes app. C

\section{$\lambda_1 \rightarrow \lambda_2$ Boundary State Amplitude}
% copy notes app. B

\section{Alternative Approach to ${\rm DN} \rightarrow \lambda$ Amplitude}
% copy notes app. A

\bibliographystyle{plain}
\bibliography{bCFT}

\end{document}

%%% Local Variables: 
%%% TeX-PDF-mode: t
%%% End:

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[compact]{titlesec}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{calc,fadings,decorations.pathreplacing,shapes,shapes.multipart,arrows,shapes.misc,intersections,positioning}
\usepackage{wrapfig}
\usepackage{bm}
\usepackage{todonotes}

\graphicspath{{./}{./images/}}

\renewcommand{\vec}[1]{\boldsymbol{\mathbf{#1}}}
\newcommand{\tr}[0]{\text{tr}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}

\tikzset{
    partial ellipse/.style args={#1:#2:#3}{
        insert path={+ (#1:#3) arc (#1:#2:#3)}
    }
}

\textwidth = 6.5 in
\textheight = 9 in
\oddsidemargin = 0.0 in
\evensidemargin = 0.0 in
\topmargin = 0.0 in
\headheight = 0.0 in
\headsep = 0.0 in
\parskip = 0.2in
\parindent = 0.0in

% configure hyperref to remove ugly boxes from links
\definecolor{darkblue}{rgb}{0.1,0.2,0.6} \definecolor{darkred}{rgb}{0.8,0.1,0.2}
\usepackage[colorlinks,citecolor=darkblue,linkcolor=darkred,urlcolor=darkblue]{hyperref}

\title{Boundary Conformal Field Theory}
\author{Tianci Zhou}

\begin{document}
\maketitle
\large

\section{Conformal Interface of Free Boson}
% flatex input: [boson_interface.tex]
\label{sec:var-boson}
[Section 2.1-2.2 of \cite{bachas_permeable_2002}.]

Let's consider the conformal interface connecting two possibly different free boson CFTs. Suppose the interface is located at $x = 0$ that glues the two theories in such a way that 
\begin{equation}
\begin{bmatrix}
\partial_t \phi\\
\partial_x \phi\\ 
\end{bmatrix}_{x = 0^-} 
 = M \begin{bmatrix}
\partial_t \phi\\
\partial_x \phi\\ 
\end{bmatrix}_{x = 0^+} 
\end{equation}
One may write the field on the left/right as $\phi^1$($\phi^2$), and then the gluing condition is
\begin{equation}
\partial_{\mu} \phi^1 = M_{\mu\nu} \partial_{\nu} \phi^2 
\end{equation}
The interface is now penetrable, and condition \eqref{eq:stress-cond} is weakened that only requires continuity of the momentum across the interface. From the explicit expression
\begin{equation}
T^{xt} = - g \partial_x \phi \partial_t \phi  = -g(\partial_{\mu} \phi \sigma^x_{\mu\nu}  \partial_{\nu} \phi ) 
\end{equation}
we have the relation
\begin{equation}
\partial_{\mu} \phi^2 \sigma^x_{\mu\nu}  \partial^2_{\nu} \phi -  \partial_{\mu} \phi^1 \sigma^x_{\mu\nu}  \partial^1_{\nu} \phi = 
\partial_{\mu} \phi^2 [\sigma^x_{\mu\nu} - M^T  \sigma^x M)_{\mu\nu} ]  \partial_{\nu} \phi^2 = 0
\end{equation}
For generic field configuration $\phi^2$, the condition is satisfied only when
\begin{equation}
\sigma^x = M^T \sigma^x M 
\end{equation}
By diagonalizing $\sigma^x$ and doing corresponding orthogonal transformation on $M$, 
\begin{equation}
\sigma^z = ( OMO^T  )^T \sigma^z ( OMO^T )  \quad 
O = \frac{1}{\sqrt{2}} 
\begin{bmatrix}
1 & 1 \\
1 & -1 \\                       
\end{bmatrix}
\end{equation}
we realize $O M O^T$ is in the Lorentz group $O( 1, 1 )$, whose 4 disconnected components that are determined by the sign of determinants and the $00$ element. A natural boost parameterization are 
\begin{equation} 
\Lambda = O M O^T = \pm 
\begin{bmatrix}
\cosh \beta & \sinh \beta \\
\sinh \beta & \cosh \beta \\  
\end{bmatrix}
\quad \pm 
\begin{bmatrix}
\cosh \beta & -\sinh \beta \\
\sinh \beta & -\cosh \beta \\  
\end{bmatrix}
\end{equation}
Reverting back to $M$, we have $\lambda = e^{-\beta}$
\begin{equation}
M_1 = \pm 
\begin{bmatrix}
\lambda^{-1} & 0 \\
0 & \lambda \\
\end{bmatrix}
\quad 
M_2 = \pm 
\begin{bmatrix}
0 & \lambda\\
\lambda^{-1} & 0 \\
\end{bmatrix}
\end{equation}
The $\pm$ branches in each $M$ can be combined if we set $\lambda = \text{tan} \theta$ for $\theta \in [- \frac{\pi}{2}, \frac{\pi}{2} ] $.

The physical significance of $\theta$ can be seen in the following scattering picture. The solutions of equation of motion are the left and right moving waves. The derivative $\partial_{-} = \partial_t - \partial_x$ removes the left moving component($x+t$) and hence can generate right moving fields $\partial_{-} \phi$. The process of right moving $\phi^1$ combined with left moving $\phi^2$ to generate a left moving $\phi^1$ and right moving $\phi^2$
\begin{equation}
\partial_{-} \phi^1 + \partial_{+} \phi^2 \rightarrow \partial_{+} \phi^1 + \partial_{-} \phi^2
\end{equation}
can be described by the scattering matrix
\begin{equation}
\begin{bmatrix}
\partial_{+} \phi^1 \\
\partial_{-} \phi^2 \\
\end{bmatrix}
 = S
\begin{bmatrix}
\partial_{-} \phi^1 \\
\partial_{+} \phi^2 \\
\end{bmatrix}
\end{equation}
After some linear algebra, we find that $2\theta$ is the angle that parameterize the scattering matrix\footnote{I adopt several different conventions from \cite{bachas_permeable_2002}. 1. I put $\partial_t$ as the first entry of the vector. 2. The matrices $M(\lambda)$ is actually $M(\lambda^{-1} )$ in \cite{bachas_permeable_2002}. These two cancel out and the resulting gluing conditions are the same. 3. I take $\partial_{-} \phi^1, \partial_{+} \phi^2$ as incoming wave, so that the $S$ matrix maps it to the outgoing waves, while \cite{bachas_permeable_2002} use the opposite: they obtain $S^{-1}$. Incidentally, $S = S^{-1}$. 4. I take $\partial_{-} = \partial_t - \partial_x $, while \cite{bachas_permeable_2002} seems to take $\partial_{-} = \partial_x - \partial_t$. Interchanging $x$ and $t$ amounts to change $\lambda$ to $\lambda^{-1}$, or $\theta$ to $\frac{\pi}{2}- \theta$, which indeed converts $S$ here to the $S$ in \cite{bachas_permeable_2002}. }
\begin{equation}
\label{eq:S1-S2}
S_1 =
\begin{bmatrix}
\cos 2 \theta & \sin 2 \theta \\
\sin 2 \theta & - \cos 2 \theta     
\end{bmatrix}
\qquad
S_2 = 
\begin{bmatrix}
-\cos 2 \theta & \sin 2 \theta \\
-\sin 2 \theta & - \cos 2 \theta   
\end{bmatrix}
\end{equation}

\subsection{Example: Free Boson with Different Compactification Radii}

[Section 2.2 of \cite{bachas_permeable_2002}.]

Suppose $\phi^1$ and $\phi^2$ are compact Bosons with compactification radii $2\pi R_1$ and $2\pi R_2$. We can rescale them to a single field 
\begin{equation}
\phi = \left\lbrace
       \begin{aligned}
         R_1^{-1} \phi^2  & \quad  x < 0 \\
         R_2^{-1} \phi^2  & \quad x > 0  \\
       \end{aligned} \right. 
\end{equation}
such that $\phi$ is a compact boson on the whole plane with radius $2\pi$, whose action(in Euclidean time) reads
\begin{equation}
S = \frac{g}{2} R_1^2 \int_{x \le 0 } \left(  \nabla \phi \right)^2 d\tau dt  + \frac{g}{2} R_2^2 \int_{x > 0 } \left(  \nabla \phi  \right)^2 d\tau dt 
\end{equation}
Both the bulk action as well as the interface should be invariant under the conformal transformation. We do such a conformal transformation, which induces a change on the field $\phi \rightarrow \delta \phi $, and since the bulk is invariant, we only need to check the boundary term
\begin{equation}
S = \frac{g}{2} \int_{x = 0 } ( R_1^2 \partial_x \phi\big|_{x = 0^{-}}   - R_2 ^2 \partial_x \phi \big|_{x = 0^{+}} ) \delta \phi  d\tau = 0
\end{equation}
The boundary condition
\begin{equation}
R_1^2 \partial_x \phi\big|_{x = 0^{-}}  = R_2 ^2 \partial_x \phi \big|_{x = 0^{+}}
\end{equation}
which makes any variation vanish must be conformal invariant. In terms of the $\phi^1$, $\phi^2$ fields
\begin{equation}
\partial_x \phi^1 = \frac{R_2}{R_1} \partial_x \phi^2 
\end{equation}
According to our previous analysis, it corresponds to $M_1$ with $\lambda = \frac{R_2}{R_1} = \tan \theta$, namely
\begin{equation}
\label{eq:cpt_boson_bd}
\partial_t ( \cos \theta \phi^1  - \sin \theta \phi^2 ) = 0 \qquad \partial_x ( \sin \theta \phi^1  - \cos \theta \phi^2 ) = 0
\end{equation}

%%% Local Variables:
%%% TeX-master: "bCFT_notes"
%%% TeX-PDF-mode: t
%%% End:

% flatex input end: [boson_interface.tex]

% configure hyperref to remove ugly boxes from links

\subsection{Folding Trick and Boundary State}
% flatex input: [folding.tex]

[Section 2.3-2.4 of \cite{bachas_permeable_2002}]

We can fold the field $\phi^2$ to the left half plane on top of $\phi^1$, then the boundary at $x = 0$ is impenetrable for the tensor theory and therefore is a boundary state of Boson.

The folding takes $x$ to $-x$ in $\phi^2$, so its $x$ derivative in the boundary condition \eqref{eq:cpt_boson_bd} will change sign and becomes\footnote{Change $\theta$ to $\frac{\pi}{2} - \theta$ to compare relevant result with in \cite{bachas_permeable_2002}. I believe the \cite{bachas_permeable_2002} made a mistake here. Nevertheless the Casimir energy is insensitive to this change.},
\begin{equation}
\partial_t ( \cos \theta \phi^1  - \sin \theta \phi^2 ) = 0 \qquad \partial_x ( \sin \theta \phi^1  + \cos \theta \phi^2 ) = 0
\end{equation}
It looks like the rotated field within $\partial_t$ takes Dirichlet boundary condition and the other orthogonal field within $\partial_x $ takes Neumann boundary condition, so we have\footnote{We will deal with the winding sector in Sec.~\ref{sec:winding}}
\begin{equation}
\label{eq:rot-D-N}
\begin{aligned}
\cos  \theta a^1_n - \sin \theta a^2_n  &= + \left( \cos  \theta \bar{a}^1_{-n} - \sin \theta \bar{a}^2_{-n} \right)\\
\sin  \theta a^1_n + \cos \theta a^2_n  &= - \left( \sin  \theta \bar{a}^1_{-n} + \cos \theta \bar{a}^2_{-n} \right) 
\end{aligned}
\end{equation}
The left and right sides can be regarded as two new sets of $a^1$ and $a^2$ whose commutation relation is preserved by the orthogonal rotation. Consequently, the boundary state is
\begin{equation}
\label{eq:bd_state}
\begin{aligned}
| B \rangle &= \exp\Big\{ \sum_{n > 0 } \frac{1}{n} (\cos  \theta a^1_{-n} - \sin \theta a ^2_{-n} )(\cos  \theta \bar{a}^1_{-n} - \sin \theta \bar{a}^2_{-n} ) \\
& \,\,  \qquad \qquad -\frac{1}{n} (\sin  \theta a^1_{-n} + \cos \theta a ^2_{-n} )(\sin  \theta \bar{a}^1_{-n} + \cos \theta \bar{a}^2_{-n} )
\Big\} | 0 \rangle \\
& = \exp\Big\{ \sum_{n > 0 } \frac{1}{n} \left( \cos 2\theta a^1_{-n} \bar{a}^1_{-n}  - \cos 2\theta a ^2_{-n} \bar{a}^2_{-n}   
- \sin 2 \theta a ^2_{-n}\bar{a}^1_{-n}  - \sin 2 \theta a ^1_{-n}\bar{a}^2_{-n}  \right ) \Big\}| 0 \rangle \\
& =  \exp\Big\{ \sum_{n > 0 } \frac{1}{n}
\begin{bmatrix}
a_{-n}^1\\
a_{-n}^2\\                              
\end{bmatrix}
S_1
\begin{bmatrix}
\bar{a}_{-n}^1  \bar{a}_{-n}^2
\end{bmatrix} \Big\}
\end{aligned}
\end{equation}

%%% Local Variables:
%%% TeX-master: "bCFT_notes"
%%% TeX-PDF-mode: t
%%% End:
% flatex input end: [folding.tex]

% configure hyperref to remove ugly boxes from links

\section{Compact Boson Winding Modes}
\label{sec:winding}
% flatex input: [D_and_N.tex]

\subsection{Dirichlet and Neumann Boundary Conditions}

[Section 2 of \cite{bachas_fusion_2008}, Section 6.3.5 of \cite{di_francesco_conformal_1997}]

The winding modes of compact boson determines the conformal dimensions of the primary fields. It therefore restrict possible bcc operators on the boundary. In this section we work the simple Dirichlet and Neumann conditions for the winding modes.

{\bf Mode Expansion:} 
Suppose the boson is compactified as $\phi \rightarrow \phi + 2\pi R$, then mode expansion in Eq.~\ref{eq:boson-mode-exp} will have a different zero mode\footnote{The sign of the $x$ term is different from Eq. (6.91) in \cite{di_francesco_conformal_1997}, but calculation later shows that the $-$ sign is correct to give the $(\frac{n}{4\pi gR} + \frac{1}{2} \frac{m}{R})$ combination for $z$. }  
\begin{equation}
\begin{aligned}
\phi( x, t ) &= \phi_0 - \frac{2\pi m R}{L}x + \frac{\pi_0}{gL} t  + \text{oscillator part}  \\
&= \phi_0 - \frac{2\pi m R}{L}x + \frac{n}{gLR} t  + \text{oscillator part}  \\
\end{aligned}
\end{equation}
where the conjugate momentum $\pi_0$ takes discrete eigenvalues $\frac{n}{R}$. A particle living on unit circle $[0, 2\pi]$ have integer($m \hbar$) angular momentum(conjugate momentum), and so momentum of Boson living on $[0, 2\pi R]$ will have $\frac{n}{R}$ as its eigenvalues.

The left and right mode decomposition is again done by complex variables
\begin{equation}
z = \exp( 2 \pi i \frac{t - x}{L}) \qquad \bar{z} = \exp( 2 \pi i \frac{t + x}{L})
\end{equation}
which leads to
\begin{equation}
\label{eq:boson-mode-exp}
\begin{aligned}
\phi( z, \bar{z}) = &\phi_0 -i \left( \frac{n}{4\pi g  R} + \frac{m R }{2} \right)  \ln z + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{a_n}{n} z^{-n } \\
&-i \left( \frac{n}{4\pi g R} - \frac{m R }{2} \right)  \ln \bar{z} + \frac{i}{\sqrt{4\pi g}} \sum_{n\ne 0 } \frac{\bar{a}_n}{n} \bar{z}^{-n } 
\end{aligned}
\end{equation}
From the holomorphic derivative 
\begin{equation}
i \partial_z \phi =  \sum_n \frac{1}{\sqrt{4\pi g}} a_n z^{-n-1}  \qquad a_0 = \sqrt{ 4 \pi g } \left( \frac{n}{4\pi g R} + \frac{m R }{2} \right)
\end{equation}
we make up the zero mode term in $L_0$ is absent for free boson, 
\begin{equation}
L_0 = \sum_{n> 0 } a_{-n} a_n + \frac{1}{2} a_0^2 =   2\pi g \left( \frac{n}{4\pi g R} + \frac{m R }{2} \right)^2 + \sum_{n> 0 } a_{-n} a_n
\end{equation}
The ground state now has dimension $h = 2\pi g \left( \frac{n}{4\pi g R} + \frac{m R }{2} \right)^2$.

{\bf Dirichlet and Neumann}:

Now that we have a legitimate $a_0$ that behaves similar with other oscillator modes, we can then impose the same Dirichlet condition in Eq.~\ref{eq:D-mode-cond}, on the unit circle, the logarithmic term gives 
\begin{equation}
 -i \frac{1}{\sqrt{ 4\pi g}}  ( a_0 \ln z  + \bar{a}_0 \ln \bar{z} )\Big|_{\text{unit circle }} = 0 \quad \implies \quad a_0 - \bar{a}_0 = 0  \quad \implies \quad m = 0
\end{equation}
The boundary states satisfying this boundary condition can be a linear superposition of the zero winding states. Since it's Dirichlet, it is an eigenstate of $\hat{\phi}_0$\footnote{We have quantized the theory such that $[\phi_0, \frac{n}{R}] = i $. },
\begin{equation}
|{\rm D} \rangle  = g_{\,\!_\text{D}}  \prod_{n > 0 } \exp(\frac{1}{k} a_k^{\dagger} \bar{a}_{-k}^{\dagger} )| \phi_0 \rangle \quad | \phi_0 \rangle = \sum_{n \in \mathbb{Z}} e^{-i \frac{n}{R}\phi_0 } | n, m = 0 \rangle  
\end{equation}
With this one can show
\begin{equation}
\phi( x, t = 0 ) | {\rm D} \rangle = \phi_0 | {\rm D} \rangle
\end{equation}

Similarly, the Neumann boundary condition now has the $n = 0$ term in Eq.~\ref{eq:N-mode-cond}
\begin{equation}
 a_0 + \bar{a}_0 = 0  \quad \implies \quad n = 0 
\end{equation}
the resulting boundary state is a linear superposition over the winding sector
\begin{equation}
| {\rm N} \rangle = g_{\,\!_\text{N}} \prod_{n > 0 } \exp(\frac{1}{k} a_k^{\dagger} \bar{a}_{-k}^{\dagger} )| \bar{\phi}_0 \rangle \quad | \bar{\phi}_0 \rangle = \sum_{n \in \mathbb{Z}} e^{i m \bar{\phi}_0 } | n = 0, m \rangle 
\end{equation}
In fact, Neumann becomes Dirichlet in the dual field, so $\bar{\phi}_0$ is related to the boundary value of the dual field.

One can check that this indeed satisfies the Neumann boundary condition
\begin{equation}
\partial_t \phi( x, t = 0 ) | {\rm N } \rangle = 0
\end{equation}

%%% Local Variables:
%%% TeX-master: "bCFT_notes"
%%% TeX-PDF-mode: t
%%% End:
% flatex input end: [D_and_N.tex]

% configure hyperref to remove ugly boxes from links
\subsection{Gluing Condition for Winding Modes}
% flatex input: [glue_zero.tex]
[Appendix A of Oshikawa\cite{oshikawa_boundary_2010}]

In Sec.~\ref{sec:var-boson}, we use variational approach to find conformal invariant boundary conditions, but the resulting equation \eqref{eq:cpt_boson_bd} do not provide information about the winding sector. The variational method fails because winding is a global properties of the Boson configuration, meaning insensitive to the local perturbation.

Here we present a general treatment about the winding modes. From the discussion of the Dirichlet and Neumann boundary condition in previous subsection, it seems that the constraints on the oscillator modes can be naturally extended to the zero mode for $n = 0$. We can show that this is in compliance with the conformal invariance.

Suppose in the junction we have a boundary condition that result in the following scattering relation
\begin{equation}
\begin{bmatrix}
\partial_{+} \phi^1 \\
\partial_{-} \phi^2 \\
\end{bmatrix}
 = S
\begin{bmatrix}
\partial_{-} \phi^1 \\
\partial_{+} \phi^2 \\
\end{bmatrix}
\end{equation}
the conformal invariance constraint gives two solutions $S_1$ and $S_2$ in Eq.~\eqref{eq:S1-S2}. Imagining that we fold $\phi^2$ on top of $\phi^1$, the $x$ derivative on $\phi^2$ then changes sign, we therefore have
\begin{equation}
\begin{bmatrix}
\partial_{+} \phi^1 \\
\partial_{+} \phi^2 \\
\end{bmatrix}
 = S
\begin{bmatrix}
\partial_{-} \phi^1 \\
\partial_{-} \phi^2 \\
\end{bmatrix}
\end{equation}
It it convenient to work in the holomorphic mode expansion \eqref{eq:boson-mode-exp} for the left and right separation. Specifically
\begin{equation}
\partial_{+} = \frac{4\pi i }{L} \bar{z} \partial_{\bar{z}} \qquad \partial_{-} = \frac{4\pi i }{L} z\partial_{z}
\end{equation}
and
\begin{equation}
\sum_{n \in \mathbb{Z}}  
\begin{bmatrix}
\bar{a}^1_{n} \bar{z}^{\scalebox{0.5}[0.8]{\( - \)}n}\\ 
\bar{a}^2_{n} \bar{z}^{\scalebox{0.5}[0.8]{\( - \)}n} 
\end{bmatrix}
 = S
\sum_{n \in \mathbb{Z}}
\begin{bmatrix}
a^1_n z^{\scalebox{0.5}[0.8]{\( - \)}n} \\
a^2_n z^{\scalebox{0.5}[0.8]{\( - \)}n} \\
\end{bmatrix}
\end{equation}
We impose boundary condition at $t = 0$\footnote{In Sec.~\ref{subsec:free-boson}, we interchange $x$ and $t$, and impose boundary condition at $x = 0$. For whatever convention, the boundary is on the unit circle $|z| = 1$. }, so $z$  is on the unit circle and $\bar{z} = \frac{1}{z}$. By comparing the modes(Fourier series on circle), we have
\begin{equation}
\label{eq:mode-eq}
a_n^i - (S^{\scalebox{0.5}[0.8]{\( - \)}1})_{ij} \bar{a}_{\scalebox{0.6}[0.6]{\( - \)}n}^j = 0
\end{equation}
This is clearly a generalization of the Dirichlet and Neumann boundary conditions, where the orthogonal matrix $S$ is replaced by $\pm \mathbb{I}$. In fact, the rotation does not change the quadratic relation
\begin{equation}
\sum_i a^i_n a^i_m =  \sum_i \bar{a}_{\scalebox{0.6}[0.6]{\( - \)}n}^i \bar{a}_{\scalebox{0.6}[0.6]{\( - \)}m}^i
\end{equation}
Hence for the quadratics in the Virasolo generators
\begin{equation}
\begin{aligned}
L_n &= \frac{1}{2} \sum_i  \sum_{m > -1 } (a^i_{n-m} a^i_m  + a^i_{-m} a^i_{n+m } ) - \frac{1}{2} a^i_0 a^i_n 
\end{aligned}
\end{equation}
the cancellation works the same way,
\begin{equation}
\begin{aligned}
L_n - \bar{L}_{-n} &= \frac{1}{2} \sum_i \sum_{m > -1} ( a^i_{n-m} a^i_m + a^i_{-m} a^i_{n+m} - \bar{a}^i_{-n-m} \bar{a}^i_{-m} - \bar{a}^i_{m} \bar{a}^i_{-n+m }  )  - \frac{1}{2}( a_0^i a_n^i - \bar{a}_0^i \bar{a}^i _{-n})\\
& = \frac{1}{2} \sum_i \sum_{m > -1} ( a^i_{n-m} a^i_m  - \bar{a}^i_{-n+m}\bar{a}^i_{-m})+ (a^i_{-m} a^i_{n+m} - \bar{a}^i_{m} \bar{a}^i_{-n -m }  )\\
& = 0 
\end{aligned}
\end{equation}
We now specialize to the two cases $S = S_1$ and $S_2$.

{\bf Boson $\lambda$ Junction: $S = S_1$}

We need to solve the $n = 0$ of \eqref{eq:mode-eq} for $S^{-1} = S_1^{-1} = S_1$\footnote{Recall that the solution of Eq.~\eqref{eq:mode-eq} for the nonzero mode is $\exp(\frac{1}{n} a_{-n}^{i} S^{-1}_{ij} a_{-n}^j |0\rangle)$. In Eq.~\eqref{eq:R-bs} we do have $R = S_1$. } and
\begin{equation}
a^i_0 = \sqrt{4\pi g}  \frac{1}{4\pi} (2\pi m_i R_i + \frac{1}{g} \frac{n_i}{R_i})
\end{equation}
For notational simplicity, we introduce the compactification lattice and its dual\cite{oshikawa_boundary_2010}
\begin{equation}
\label{eq:lattice}
\vec{M} = (m_1 2 \pi R_1, m_2 2\pi  R_2)^\top, \quad  \vec{M}^* = (\frac{n_1}{R_1}, \frac{n_2}{R_2})^\top
\end{equation}
the constraint then becomes 
\begin{equation}
  a_0^i - S^{-1} _{ij} \bar{a}_{0}^j = 0 \quad \implies \quad ( \vec{M} + \frac{1}{g}\vec{M}^* ) = S_1 ( -\vec{M} + \frac{1}{g}\vec{M}^* )
\end{equation}
which is basically the two dimensional case of the multi-component Boson constraints in Eq.~(86) of \cite{oshikawa_boundary_2010}.

Given the $S_1$ matrix in Eq.~\eqref{eq:S1-S2}, we have
\begin{equation}
1 + S_1 = 2  
\begin{bmatrix}
\cos^2 \theta & \sin \theta \cos\theta \\
\sin \theta \cos \theta  & \sin^2 \theta \\
\end{bmatrix}
\quad 
1 - S_1 = 2
\begin{bmatrix}
\sin^2 \theta & -\sin \theta \cos\theta \\
-\sin \theta \cos \theta  & \cos^2 \theta \\
\end{bmatrix}
\end{equation}
both have determinant zero. So the solution of the two lattice vectors in 
\begin{equation}
( 1 + S_1) \vec{M} = -( 1 - S_1 ) \frac{1}{g} \vec{M}^*
\end{equation}
must be the null vectors of the corresponding matrices, i.e. 
\begin{equation}
\vec{M} = ( \cos \theta, -\sin \theta )^\top \qquad \vec{M}^{*} = ( \sin \theta, \cos \theta )^\top 
\end{equation}
In terms of the winding numbers
\begin{equation}
  \tan \theta =  \frac{n_1 R_2}{n_2 R_1 } = -\frac{m_2 R_2}{ m_1 R_1}
\end{equation}
One can take a pair of coprime integers $k_1$ and $k_2$($k_1>0$), such that $-\frac{m_1}{m_2} = \frac{k_1}{k_2}$. That determines all the possible winding numbers of the basis\footnote{\cite{bachas_fusion_2008} takes $-S_1$ as the S matrix, so they have $\vec{M} = ( \cos \theta, \sin \theta)^\top $ and $\tan \theta = -\frac{n_1 R_2}{n_2 R_1 } = \frac{m_2 R_2}{ m_1 R_1} = \frac{k_2 R_2}{k_1 R_1}$ for $\frac{m_1}{m_2} = \frac{k_1}{k_2}$. And this is consistent with their parameterization  $ \left\lbrace
  \begin{aligned}
    m_1 = k_1 M  & \quad n_1 = k_2 N  \\
    m_2 = k_2 M &  \quad n_2 = -k_1 N \\
  \end{aligned} \right. $ }. The linear superposition is beyond conformal invariance, which should be determined by Cardy's consistency condition.

This set of boundary conditions can be viewed as Dirichlet and Neumann on the rotated basis, hence a reasonable conjecture is also the Fourier sum of the basis(constrained by $S_1$)
\begin{equation}
g_{\,\!_{S_1}} \sum_{S_1} e^{i n_1 \phi_0 - i m_1 \bar{\phi}_0 } | n_1, m_1  \rangle | n_2, m_2  \rangle 
\end{equation}

{\bf The T-dual Boundary State $S = S_2$}

Now we take $S = S_2$, the zero mode condition becomes
\begin{equation}
( \vec{M} + \frac{1}{g}\vec{M}^* ) =  S_2^{-1}  ( -\vec{M} + \frac{1}{g}\vec{M}^* )
\end{equation}
the solution is
\begin{equation}
\vec{M} =  \frac{1}{g} \frac{1 - S_2}{1 + S_2} \vec{M}^{*} = \frac{1}{g}  \frac{1}{ 1 - \cos 2\theta}
\begin{bmatrix}
  0 & - \sin 2 \theta \\
\sin 2\theta & 0 \\
\end{bmatrix} \vec{M}^*
 = \frac{\cot \theta}{g} \begin{bmatrix}
  0 & - 1 \\
1 & 0 \\
\end{bmatrix}\vec{M}^*
\end{equation}
Using the basis vectors in Eq.~\ref{eq:lattice}, we have
\begin{equation}
\begin{bmatrix}
m_1\\
m_2\\
\end{bmatrix}
 = \frac{2 \cot \theta}{ 4\pi g  R_1 R_2 }
\begin{bmatrix}
-n_2 \\
n_1 
\end{bmatrix}
\end{equation}
Taking the same coprime interger $\frac{m_2}{n_1} = \frac{k_2}{k_1}$, we have the angle\footnote{It takes some effort to match the results with \cite{bachas_fusion_2008}. We both use $\frac{k_2}{k_1}$ the same way, so the parameterization is the same. They use $-S_2$ as oppose to $S_2$ to be the S matrix, so $\vec{M} = \frac{1}{g} \frac{1 + S_2}{1 - S_2} = \frac{\tan \theta}{g}\begin{bmatrix}
  0 & - 1 \\
1 & 0 \\
\end{bmatrix} \vec{M}^*$, their $\tan \theta$ is my $\cot \theta = \frac{k_2}{2k_1 } 4\pi g R_1 R_2$. They use $R \rightarrow \frac{1}{2R}$ as T-duality transformation. If they were to use $R \rightarrow \frac{1}{2R}$(this point corresponds to $g = \frac{1}{4\pi}$), then their $\tan \theta = \frac{k_2}{2 k_1} R_1 R_2$ which will be the same as our $\cot \theta$. So we agree.},
\begin{equation}
  \tan \theta = \frac{2 k_1}{k_2} \frac{1}{4 \pi g R_1 R_2}
\end{equation}
This state can be obtained by taking T duality for one of the bosons, hence it is a Dirichlet/Neumann boundary conditions for these two Bosons. It is then reasonable to use Fourier sum as the physical boundary state
\begin{equation}
g_{_{\,\!_{S_2}}}\sum_{S_2} e^{i n_1 \phi_0 - i m_1 \bar{\phi}_0 } | n_1, m_1  \rangle | n_2, m_2  \rangle 
\end{equation}

{\bf The $g$ Factor}:

The $g$ factor can only be determined by Cardy condition, which means that the occurrence $n^h_{ab}$ for each irreducible representation
\begin{equation}
Z_{ab} = \langle a | e^{- \beta  H }  | b \rangle  = \sum_{h} n_{ab}^h \chi_h 
\end{equation}
is an non-negative integer.

Since the character for the compact boson theory is known, we can just compute the amplitude, say $Z_{\lambda_1, \lambda_2}$ adjust the coefficient such the occurrence is an integer. \cite{bachas_fusion_2008} contains a calculation for Dirichlet case. I will not repeat it here.

%%% Local Variables:
%%% TeX-master: "bCFT_notes"
%%% TeX-PDF-mode: t
%%% End:
% flatex input end: [glue_zero.tex]

% configure hyperref to remove ugly boxes from links
\subsection{Winding Modes Contribution to Partition Function}
% flatex input: [Z-winding.tex]

In this section, we address the concern about how the winding mode will affect the partition function.
\begin{figure}[h]
\centering
\includegraphics[width=	extwidth]{fig_part-lambda1-lambda2}\caption{Partition function between two boundary states $\lambda_1$ and $\lambda_2$}
\label{fig:part-lambda1-lambda2}
\end{figure}
